State of the Practice for Lattice Boltzmann Method Software

### 2021-12-11 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
Updates to the installation section

@@

This section presents the quantitative findings from data that was gathered
using the measurement template found in Section~\ref{measurementtemplate2} for
qualities listed in Section~\ref{softwarequalities}. The results of the AHP
analysis based on that data are also presented in this section.

Table that summarizes the software by variabilities.

@@

All of the 23 software packages that were tested have installation instructions.
As noted previously, many of the 23 software packages that were part of the
original long list of 45 packages were removed due to not including
documentation or installation instructions.

All 23 packages on the short list can be installed on some Unix-like systems.
Seven packages could be installed on Windows, and five on macOS. Operating
system compatibility is found in the documentation of 19 software packages. All
but one of the software packages, TCLB, were tested on Ubuntu for this state of
the practice assessment. TCLB was tested on CentOS, since this operating system
is mentioned in its installation instructions.

Of the software packages that were tested, most installation instructions are
located in one place, often in an instruction manual or on a web-page.
Sometimes, like with Ludwig, incomplete installation instructions are found on a
home page, with more detailed instructions located on another web-page, or
within the documentation. Maintainability and correctness of these instructions
could be improved if all the instructions were in one location.

@@

About half of the installation instructions are written as if the person doing
the installation has none of the dependent packages installed. It is common for
software packages to not list all of their dependencies despite listing some.
This was the case for many packages, including ESPResSo++, Ludwig, and LUMA.
Sometimes only an error message during the installation process informs the user
of the requirement of these additional packages. A detailed rewrite of the
installation instructions from the point of view of installation on a clean
operating system is suggested. A clean environment can be achieved for testing
purposes by using a virtual machine.

@@

Uninstallation instructions were found for only one of the software packages,
pyLBM.

>>>>

As in \citet{SmithEtAl2016}, Virtual machines (VMs) were used to provide an
optimal testing environments for each package. VMs were used because it is
easier to start with a fresh environment without having to worry about existing
libraries and conflicts. Moreover, when the tests are complete the VM can be
deleted, without any impact on the host operating system. The most significant
advantage of using VMs is to level the playing field. Every software install
starts from a clean slate, which removes ``works-on-my-computer'' errors. When
filling in the measurement template spreadsheet, the details for each VM
should be noted, including hypervisor and operating system version.

@@

Table~\ref{} presents a summary of the software that was measured.  The table
shows the differences between the packages based on features.  \wss{Add some
discussion of some example features.}  The sections below summarize how the
software packages compare based on qualities, as measured by the measurement
template.   The results of the AHP ranking are also discussed.

@@

All of the 23 software packages that were tested have installation instructions.
As noted previously, many of the 23 software packages that were part of the
original long list of 45 packages were removed due to not including
documentation or installation instructions. Of the 23 software packages that
were tested, most had installation instructions located in one place, often in
an instruction manual or on a web-page. Sometimes, like with Ludwig, incomplete
installation instructions are found on a home page, with more detailed
instructions located on another web-page, or within the documentation.
Maintainability and correctness of these instructions could be improved if all
the instructions were in one location.

All 23 packages on the short list can be installed on some Unix-like systems.
Seven packages could be installed on Windows, and five on macOS. Operating
system compatibility is found in the documentation of 19 software packages. All
but one of the software packages (TCLB) were tested on Ubuntu for this state of
the practice assessment. TCLB was tested on CentOS, since this operating system
is mentioned in its installation instructions.

@@

About half of the installation instructions are written as if the person doing
the installation has none of the dependent packages installed. Unfortunately,
software packages, like ESPResSo++, Ludwig, and LUMA, frequently don't list all
of their dependencies, or provide only a partial list. Sometimes only an error
message during the installation process informs the user of the requirement of
these additional packages. A detailed rewrite of the installation instructions
from the point of view of installation on a clean operating system is suggested.
A clean environment can be achieved for testing purposes by using a virtual
machine.

@@

Uninstallation instructions were found for only one of the software packages: pyLBM.
